\bf\mftitle

### 2011-01-15 doc/jInfer/architecture/architecture.tex
3154619 Create documentation for jInfer architecture - example of inference process - corrected as rio said

	      <xs:element name="info" minOccurs="0" maxOccurs="1" type="xs:string"/>
	      <xs:element name="more" minOccurs="1" maxOccurs="3" type="xs:string"/>

@@

	<xs:element name="info">
	      <xs:element name="note" minOccurs="1" maxOccurs="1" type="xs:string"/>
	<xs:element name="note">

@@

	<xs:element name="more">

>>>>

	      <xs:element name="info" minOccurs="0" maxOccurs="1">
	            <xs:element name="note" minOccurs="1" maxOccurs="1">

@@

	      <xs:element name="more" minOccurs="1" maxOccurs="3"/>

@@
